\documentclass[a4paper,11pt,english]{letter}

\usepackage{labo_lettre}
\usepackage{textcomp}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage[textheight=55em,bmargin=35mm, footskip=20mm]{geometry}
\thispagestyle{empty}

\usepackage{amsmath,amssymb}

\def\destinataire{%
  A.M. \textsc{Colubi}, E.J. \textsc{Kontoghiorghes} \& B.U. \textsc{Park}, Editors
}

\def\adresse{
  Julien \textsc{Chiquet}\\
  MIA Paris -- UMR 518 AgroParistech/Inra \\
  16 rue Claude Bernard, 75231 Paris Cedex 05, France \\[2ex]

  E-mail: \url{julien.chiquet@inra.fr}
}

\begin{document}

\begin{letter}

\signature{Julien Chiquet (on behalf of the authors) }

\opening{Dear Editors,}

\objet[object]{Submission of an original manuscript to CSDA}

Please find, here enclosed, our manuscript entitled \emph{Sparsity by
  Worst-Case Penalties}, which we submit to \textit{Computational
  Statistics \& Data Analysis}.

Sparse methods are now ubiquitous in statistics and statistical
learning. An important part of the literature is still dedicated to
crafting new sparsity-inducing penalties, which often require new
optimization procedures with varying complexity. In our manuscript, we
introduce a new interpretation of sparsity and an unifying view for a
large family of penality-based approaches, thus providing additional
insight on these methods. More importantly, this view paves the way
for an unifying optimization strategy. We implement this strategy for
the popular elastic-net and compare our algorithm with existing
implementations. In particular, we show that our method provides very
accurate solutions. This accuracy is required for the correctness
of the support of the solution and is not always met by existing
softwares.

We feel  that this work  might be of interest  to the readers  of your
journal and is in its scope.

We confirm that  this manuscript has not been  published elsewhere and
is not currently  under consideration by another  journal. All authors
have approved  the manuscript  and agree with  its submission  to your
journal.

\closing{Sincerely yours,}

\end{letter}

\end{document}
